---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SimpLin

<!-- badges: start -->
<!-- badges: end -->

The goal of SimpLin is to provide a fast and simple tool for fitting simple linear regression models, powered by a C++ backend using RcppArmadillo. This package was created as part of the STAT 600 Statistical Computing course at CSU.

## Installation

You can install the development version of SimpLin from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ZYChenxz/SimpLin")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SimpLin)
set.seed(600) 
x_vals <- 1:20
y_vals <- 3 * x_vals + rnorm(20)
model_fit <- SimpLin(x_vals, y_vals)
print(model_fit)
```

This will produce a list containing all the key outputs from the linear regression model, including coefficients, standard errors, confidence intervals, residuals, and predicted values.
